\newpage

\section{Methodology} \label{methodology}
To investigate the research question, we decided to go for an explanatory research. An explanatory research is common for diving deeper into phenomena by describing and explaining the reasons for them, to give an answer why something is the way it is.  It aims to understand the essence of what is being observed, focusing on explaining processes or structures and advancing knowledge about it. This type of research connects various factors and elements to formulate general statements and involves building, testing, or revising theories\footcite[p.2]{adams_research_2014}.
In our specific case, we want to improve our knowledge about something we do already have some information about. The objective we are aiming for is a mixture of providing information, to solve problems in the future and to test new services\footcite[p.3]{adams_research_2014}.
So in this chapter, we will describe how we have done our literature review at first. In the next step, we will describe the laboratory experiment and after that, the experimantel design. The next subchapter is about the setup, followed by the procedure and the research project.
The last subchapter is about our GitHub, which we have used during our experiment. 
\subsection{Literature Review} \label{literature_review}
\input{chapter/chapter_3/literature_review.tex}
\subsection{Laboratory Experiment} \label{laboratory_experiment}
\subsubsection{Experimental Design} \label{experimental_design}
\input{chapter/chapter_3/experimental_design.tex}
\subsubsection{Setup} \label{setup}
\input{chapter/chapter_3/setup.tex}
\subsubsection{Procedure} \label{procedure}
\input{chapter/chapter_3/procedure.tex}
\subsection{Research Project} \label{research_project}
    The paper focuses on WASM. However, as Business Informatics students, we also aimed to explore professional collaboration in academic paper writing. We embraced the challenge of writing the paper using LaTeX, which required learning LaTeX syntax, setting up and structuring a LaTeX project, and understanding LaTeX source management.

    Furthermore, the paper was collaboratively developed among the three researchers. We created a GitHub repository for the entire LaTeX project, just like for the experiment's code. This decision provided valuable insights and learnings which is important for our academic future since it is common practice in technical scientific papers to use LaTeX with a Git version control\footcite{laverny_using_2021}\footcite{ranganath_git_2017}.

    A consequence of these decisions was our agreement to work collectively in Microsoft Visual Studio Code using the 'LaTeX Workshop' plugin by James Yu, ensuring uniform technical capabilities among us. We considered an alternative, which was using Overleaf, an online LaTeX editor. However, this would have created costs for collaborative work, which we chose to avoid.

    Subsequent chapters of this paper provide a more detailed analysis of LaTeX and GitHub, highlighting the challenges encountered during the process.
\subsubsection{Latex Project} \label{latex_project}
\input{chapter/chapter_3/latex_project.tex}
\subsubsection{Github} \label{github}
\input{chapter/chapter_3/github.tex}